% !TEX root = ../../../main/aws_topandarith.tex
\newpage
\section{Name: Lecture Title}
\subsection{Lecture 1}
\subsubsection{Lecture Name}

Enumerative Geometry: counts algebraic-geometric objects satisfying conditions over $\C$

Goal: To record information about fields of definition

Arithmetic count of the lines on a smooth cubic surface

\begin{dfn}
Cubic surface is $\{ (x,y,z) \colon f(x,y,z)=0 \}$, where $f$ is degree 3
\end{dfn}


Better: $X \subseteq \P^3= \{ [w,x,y,z] \}$, $[w,x,y,z]= [\lambda w,\lambda x, \lambda y, \lambda z]$, where $\lambda \in K^\times$
$X= \{[w,x,y,z] \colon f(w,x,y,z)=0\}$

\begin{thm}[Salmon, Cayley 1849]
Let $X$ be a smooth, cubic surface over $\C$. Then $X$ contains exactly 27 lines.
\end{thm}


\begin{ex}
Fermat
$f(w,x,y,z)= w^3+x^3+y^3+z^3$
$L= \{[S,-S,T,-T] \colon [S,T] \in \P^1\}$
$\lambda,\omega: \lambda^3=\omega^3= -1$

Lines $\{ [S,\lambda S,T,\omega T] \colon S,T \in \P^1\}$
This produces $3 \cdot 3 \cdot 3= 27$ llines
\end{ex}


Modern proof: $\gr(1,3)$, the Grassmannian parametrizing lines in $\P^3$, equivalently $W \subseteq \C^4$, $\dim W=2$

Let $S \to \gr(1,3)$ be the tautological bundle, $S_W= W$
$\sym^3 S^* \to \gr(1,3)$
$\sym^3S^*_W$ is the cubic polynomial on $W$, i.e. $\sym^3 W^*$
$F$ determines element $\sym^3(\C^4)^*$ then $f$ determines a section of $\sym^3S^*$ by $\sigma_f(W)= f\big|_W$

Note: the line $\P W$ corresponding to $W$ is in $X$ $\Leftrightarrow \sigma_f(W)=0$.

Want: to count zeros of $\sigma_f$
Euler class: $V \to M$ be a rank $r$ $\R$-vector bundle on a dimension $r$ $\R$-manifold $M$. Assume $V$ is oriented 

Choose a section $\sigma$ with only isolated zeros.
$\deg [S^{r-1},S^{r-1}] \to \Z$, homotopy classes of maps

$P \in M$, $\sigma(p)=0$
To define: $\deg_p \sigma \in \Z$

Here's how: choose local coordinates on $M$ around $p$. There's a small ball around $p$ with no other zeros. Choose local trivialization of $V$. Then $\sigma$ can be identified with a function $\sigma: \R^r \to \R^r$ given by $0 \mapsto 0$, $\sigma(\ov{B_0(1)}=0) \subset \R^r=0$
$S^{r-1}= OB_0(1) \ma{\ov{\sigma}} \partial B_0(1)= S^{r-1}$ given by $x \mapsto \sigma(x)/|\sigma(x)|$


Then $\deg_p \sigma= \deg(\ov{\sigma})$

Euler class 
$e(V)= \sum_{p: \sigma(p)=0} \deg_p \sigma$

Fact: $X$ smooth then $\deg_p \sigma=1$, then number of lines on $X= e(\sym^3S^*)$. In particular, number of lines is independent of $X$
$e(\sym^3S^*)=27$


Question: What about cubic surfaces over $\R$?

Segre in 20th century showed $X$ can have 3, 7, 15, or 27 real lines.


Segre 1942 distinguished between different hyperbolic and elliptic real lines on $X$

Recall: $L$ real line, $L \cong \P_\R^1$, $\Aut(L) \cong \P \gl_2(\R)$
$I \leftrightarrow I = \begin{pmatrix} a & b \\ c & d \end{pmatrix}$
$z \mapsto \dfrac{az+b}{cz+d}$
$\fix(I)= \{z \colon cz^2+(d-a)z+b=0\}$
either consists of 3 real points if and only if $I$ hyperbolic. a ?? conjugate pair of points elliptic.


We associate an involution $I$ to $L \subset X$ a real line on a real cubic surface.

$p \in L$
$T_p X \cap X= L \cup Q$
% Give picture
$Q \cap L=$ points $q$ such that $T_qX= T_pX= \{p,p'\}$
$I(p)= p'$

\begin{dfn}
$L$ is elliptic/hyperbolic when $I$ is 
\end{dfn}

Alternatively, spin structure.


\begin{ex}
Fermat cubic surface $x^3+y^3+z^3= -1$
% Give picture
hyperbolic
\end{ex}


\begin{thm}[Segre,Okonek,Teleman,\dots]
Number of hyperbolic lines $-$ number of elliptic lines $=3$.
\end{thm}


$\A^1$-homotopy theory (due to Morel-Voemsky)

On smooth schemes over $k$, $k$ a field.
Morel deg: $[\P^n/\P^{n-1}, \P^n/\P^{n-1}] \to G W(k)$
where $GW(k)$ is the Grothendieck-Witt$=$group completion of semiring $\oplus,\otimes$ isomorphism classes of (nondegenerate symmetric) bilinear forms $B: V \times V$, finite dimensional $k$ vector spaces

presentation:
generators: $\langle a \rangle$, $a \in k^\times$
$\langle a \rangle: k \times k \to k$, $(x,y) \mapsto axy$
relations: $\langle ab^2 \rangle= \langle a \rangle$, $b \in k^\times$
$\langle a \rangle + \langle b \rangle= \langle a+b \rangle = \langle ab(a+b) \rangle$


\begin{ex}
$GW(\C) \cong \Z$, rank, $B \mapsto \dim V$
\end{ex}


\begin{ex}
$GW(\R) \to \Z \times \Z$ by signatures $\times$ rank. Also iso to $\Z \times \Z$
% give pict
$GW(\F_q) \to \F_q^\times/(\F_q^\times)^2$ given by signatures $\times$ rank, isomorphism
\end{ex}


There is an Euler class
	\[
	e(V)= \sum_{p: \sigma(p)=0} \deg_p \sigma
	\]
$R$ field char not 2. $X$ a smooth cubic surface over $k$
line $L \subseteq X$ is a closed point of $\gr(1,3)$
$L= \{ [a,b,c,d]S+[a',b',c',d'] T \colon [S,T] \in \P^1\}$
$k(L)= k(a,b,c,d,a',b',c',d')$
$\P_{k(L)}^1 \cong L \subseteq X_{k(L)} \subseteq \P_{k(L)}^3$
Given a line $L$ on $X$, obtain involution $I \in \Aut(L) \cong \P \gl_2 k(L)$
$\fix(I)$ is either 2 $k(L)$ points or a conjugate pair of points in $k(L)[\sqrt{D}]$ for $D \in k(L)^*/(k(L)^*)^2$

\begin{dfn}
$\typ(L):= \langle D \rangle \in GW(k(L))$
\end{dfn}

Equivalent to $D= ab-cd$, $I= \two{a}{b}{c}{d}$
$\typ(L)= \langle -1 \rangle \deg I$

\begin{thm}[Kass-W.]
$\char R \neq 2$, $X$ smooth cubic surface
	\[
	\sum_{lines L of X} \tr_{k(l)/k} \typ(L)= 15 \langle 1 \rangle + 12 \langle -1 \rangle
	\]
$\tr_{k(L)/k}: GW(k(L)) \to GW(k)$ given by $(B: V \times V \to k(L)) \mapsto V \times V \ma{B} k(L) \to k$
\end{thm}

$R= \C$, apply rank, number of lines is 27
$k= \R$ apply signature
Number of hyperbolic lines $-$ number elliptic lines $=3$

\begin{cor}
$k= \F_q$
Number of elliptic lines $L$ with $k(L)= \F_{q^{2n+1}}$ plus number of hyperbolic lines with $k(L)= \F_{q^{2n+1}}$ is equivalent to 0. 
\end{cor}




























