% !TEX root = ../../../main/aws_topandarith.tex
\newpage
\section{Name: Lecture Title}
\subsection{Lecture 1}
\subsubsection{Lecture Name}
A brief review

$A$ a $k$-algebra $\to$ Hochschild complex

$\hh(A/k):= A \stackrel{k}{\leftarrow} A^{\otimes 2} \stackrel{k}{\leftarrow} A^{\otimes 3} \stackrel{k}{\leftarrow} \cdots$

$\hh_n(A/k) \leftrightarrow \Omega^n_{A/k}$

% Double complex picture

Norm sequence: $0 \ma{} \hc^-(A/k) \ma{} \hp(A/k) \ma{} \hc (A/k)[2] \ma{} 0$

If $\hh_{odd}(A/k)=0$, then also for $\hc^-,\hp,\hc$ and get
$0 \ma{} \hc^-_{2n}(A/k) \ma{} \hp_{2n}(A/k) \ma{} \hc_{2n-2}(A/k) \to 0$

$\hp_{2n}(A/k) \cong \hp_0(A/k)$

$\hp_0(A/k)$ is filtered ring with associated graded $= \hh_{2*}(A/k)$


Main theorem about smooth algebras (loday-quillen, Feign-Tsyon,Connes) If $A$ is a smooth $k$-algebra and $k \supseteq \Q$, then the norm sequence looks like $\prod_{i \in \Z} ?[2i]$, where $?$ is 
	\[
	0 \ma{} \Omega_{A/k}^{\geq i} \ma{} \Omega_{A/k}^\cdot \ma{} \Omega_{A/k}^{<i} \ma{} 0
	\]
,i.e. HP $\leftrightarrow$ de Rham cohomology 
$\hc^- \leftrightarrow$ hodge filtration

\pf Explicit map of chain complexes 
$\hh(A/k) \ma{\delta} [A \leftarrow \Omega_{A/k}^1 \leftarrow \Omega_{A/k}^2 \leftarrow \cdots]$
$a_0 \otimes \cdots \otimes a_n \mapsto \frac{1}{n!} a_0 da_1 \wedge \cdots \wedge da_n$
on $\hh_n(-)$, this splits $\epsilon: \Omega^n \to \hh_n$. 


Because smooth algebra, maps are isomorphisms. Tells that $\delta$ is quism. So looking at double complex, replace up to quism  columns by the `dumb' complex here. Know $b$ operator compatbile with de Rham so looks like sums of direct copies of de rham complexes. \qed 


HC etc in characteristic $p$

Thm: $R$ smooth over $\F_p$. Then the classical theorem is still true but the filtration is not naturally split, e.g. $\hp(R/\F_p)$ has a filtration whose graded pieces are $\Omega_{R/\F_p}^i[2i]$, $i \in \Z$.

`classical' proof: yoga if able ??

Today: Analysis if $\hp(R/\F_p)$ via perfectish map $-$ will generalize to topological case. 

Idea: Don't study smooth algebra but instead quasiregular semiperfect (qrsp) $\F_p$-algebras

$-$ big (non-noetherian)
$-$ but homologically simple

Def: An $\F_p$-algebra $A$ is qrsp if there exist

a perfect $\F_p$-algebra $B$, $B \ma{\cong} B$, $b \mapsto b^p$
a regular ideal $I \subseteq B$
$I/I^2$ is a finite projective $B/I$-module such that $B/I= A$. 


eg of regular ideal: generated by a regular sequence

Examples:
1) $\F_p[t^{1/p^\infty}]/(t)$
2) if $R$ smooth $\F_p$-algebra then its perfection $R_\perf:= \injlim R$, where limit over $x \mapsto x^p$ then $R_\perf \otimes_R \cdots \otimes_R R_\perf$ is qrsp

eg, $\F_p[t]_\perf \otimes_{\F_p[t]} \F_p[t]_\perf \cong \F_p[t^{1/p^\infty}] \otimes_{\F_p[t]} \F_p[t^{1/p^\infty}]= \F_p[t_1^{1/p^\infty}, t_2^{1/p^\infty}]/(t_1-t_2)$


Technique: form qrsp to smooth all of our homology theories $F= \hh(-/\F_p), \hc(-/\F_p)$, etc, 
$\F_p$-algebra $\to D(\F_p)$

satisfy flat descent, meaning $S \to S'$ is a faithfully flat map of $\F_p$-algebras. then $F(S) \to \tot( F(S') \stackrel{\to}{\to} F(S' \otimes_S S') \cdots)$

eg, $R$ smooth over $\F_p$, then $R \to R_\perf$ is faithfully flat. 

So: $F(R) \to \tot(F(R_\perf)) \to\to F(R_\perf \otimes_R \to R)$

all are qrsp.


Most understand The other homologies $\hc^-,\hp,\hc$ of any group qrs $\F_p$;agebar$\Q_p$


Let $A$ be qrsp

Step 1: $\hh_{odd}(A/\F_p)=0$ and $\hh_0(A)$
$\hh_k = I/I^2 I$, where $A= B/I$
$\hh_{2n}= \Gamma_A^n(I/I^2)$
$n$th divided power of $I/I^2$

$\cong \sym_A^n(I/I^2)$ but mult. is twised by ntm $m!, n!/(n!m!)$

$\to \hh_{2*}(A/\F_p) \cong \Gamma^{A^*}(I/I^2)$
Key words; cotangent complex. 

Step 2: $\hp_0(A/\F_p)$ is a filtered ring with associated graded $\Gamma_A^*(I/I^2)$
What is it?

ANswer: hcc divided power enveolppe of completed $B$ onto $A$, regular defin. able $f^n/n!$ to surject to $A$. 



Computation: $\hp(R/\F_p)$ ($R$ smooth) is buitl from copies of 
	\[
	\tot(\hp_0(R_\perf/  \F_p)) \to \to \hp_0(R_\perf \otimes \cdots
	\]
, where $R$ smooth, contributed by divided power enevelopes 

ALso show up in theory of derived de Rham cohomolology (Bhatt)

so tot is $\cong$ $\Omega_{R/\F_[}^\cdot$














































